Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-10-04 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
update plots of replciation study

setwd(ddmDir)
write.csv(df.M.hddm_m,'MS_rep_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'MS_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'MS_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'MS_rep_categ_id_hddm.csv',row.names = F)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
setwd(curDir)

@@

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
#MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)

@@

```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)
```

>>>>

setwd(ddmDir)
write.csv(df.M.hddm_m,'MS_rep_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'MS_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'MS_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'MS_rep_categ_id_hddm.csv',row.names = F)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id','df.M.ddm.v','df.C.ddm.v')
setwd(curDir)

@@

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
#MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7_rep', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)

@@

```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7_rep', task = 'id', df.C1.V.sum_rt_acc_l)
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7_rep', task = 'val', df.C1.V.sum_rt_acc_l)
```
